(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned: it's a Working Title.

### 2015-02-25 ms.tex
Mann references

\begin{document}
\title{(Working Title) Properties of the \KT\ Campaign 1 Planets, 
False Positive Probabilities, and Confirmation of $N$ Systems. You 
Were Warned it's a Working Title.}

@@

A near-infrared spectrum of EPIC 201912552 was obtained using the updated SpeX 
(uSpeX) spectrograph \citep{Rayner03} on the NASA Infrared Telescope Facility 
(IRTF) on January 29 2015 (UT). 
SpeX observations were taking using the short cross-dispersed mode and the
0.3$\times15\arcsec$ slit, which provides simultaneous coverage from 0.7 
to 2.5$\mu$m at $R\simeq2000$. 
The target was observed at two positions along the slit to subsequently subtract 
the sky background. Eight spectra were taking following this pattern, which provided 
a final S/N of $>150$ per resolving element. 
The spectrum was flat fielded, extracted, wavelength calibrated, and stacked 
using the \textit{SpeXTool} package \citep{Cushing:2004}. 
An A0V-type star was observed immediately after 
the target, which was used to create a telluric correction using the 
\textit{xtellcor} package \citep{Vacca:2003}.

An optical spectrum was obtained using the SuperNova Integral Field Spectrograph
\citep[SNIFS,][]{2002SPIE.4836...61A,Lantz:2004} on the University of Hawai'i 
2.2m telescope on the night of January 30 2015. 
SNIFS provides simultaneous coverage from 3200\AA--9700\,AA\ at a resolution 
of $\simeq1000$. Final S/N of the spectrum was $>100$ pre resolving element 
in the red ($\sim6000$\AA). 
Details of the SNIFS reduction, including dark, bias, and flat-field corrections,
cleaning the data of bad pixels and cosmic rays, and extraction of the 
one-dimensional spectrum are  described in \citet{Bacon:2001} and 
\citet{Aldering:2006}. 
Flux calibration was performed using a separate pipeline described in \citet{Mann2015}.

\teff\ was calculated by comparing our optical spectra with the CFIST
suite\footnote{http://phoenix.ens-lyon.fr/Grids/BT-Settl/CIFIST2011/} of the BT-SETTL
version of the PHOENIX atmosphere models \citep{Allard:2013}, which gave a temperature
of 3503 $\pm$ 60\,K. 
More details of this procedure are given in \citet{2013ApJ...779..188M} and
\citet{2014MNRAS.443.2561G}. 
This method was used because it is known to accurately reproduce empirical 
\teff\ values from long-baseline optical interferometry \citet{Boyajian2012}.

Metallcity was determined using the procedures from \citet{Mann2013a}. 
\citet{Mann2013a} provide empirical relations between atomic features and M dwarf
metallicity, calibrated using wide binaries. 
We adopted the weighted mean of the $H-$ and $K-$band calibrations, 
which yielded a metallicity of 0.09$\pm$0.09.

We combined the derived \teff\ and [Fe/H] values with the empirical 
\teff-[Fe/H]-$R_*$ relation from \citet{Mann2015} to compute a radius. 
Accounting for measurement and calibration errors in [Fe/H] and \teff\ we calculated 
a radius 0.394$\pm0.038R_\odot$. 
We use these parameters instead of the derived photometric properties for this target.

@@

\bibliography{exopapers; mannbib}

>>>>

\begin{document}
\title{(Working Title) Properties of the \KT\ Campaign 1 Planets, 
False Positive Probabilities, and Confirmation of $N$ Systems. You 
Were Warned: it's a Working Title.}

@@

A near-infrared spectrum of EPIC 201912552 was obtained using the updated SpeX 
(uSpeX) spectrograph \citep{Rayner03} on the NASA Infrared Telescope Facility 
(IRTF) on January 29 2015 (UT). 
SpeX observations were taking using the short cross-dispersed mode and the
0.3$\times15\arcsec$ slit, which provides simultaneous coverage from 0.7 
to 2.5$\mu$m at $R\simeq2000$. 
The target was observed at two positions along the slit to subsequently subtract 
the sky background. Eight spectra were taking following this pattern, which provided 
a final S/N of $>150$ per resolving element. 
The spectrum was flat fielded, extracted, wavelength calibrated, and stacked 
using the \textit{SpeXTool} package \citep{Cushing04}. 
An A0V-type star was observed immediately after 
the target, which was used to create a telluric correction using the 
\textit{xtellcor} package \citep{Vacca03}.

An optical spectrum was obtained using the SuperNova Integral Field Spectrograph
\citep[SNIFS,][]{Aldering02,Lantz04} on the University of Hawai'i 
2.2m telescope on the night of January 30 2015. 
SNIFS provides simultaneous coverage from 3200\AA--9700\,AA\ at a resolution 
of $\simeq1000$. Final S/N of the spectrum was $>100$ pre resolving element 
in the red ($\sim6000$\AA). 
Details of the SNIFS reduction, including dark, bias, and flat-field corrections,
cleaning the data of bad pixels and cosmic rays, and extraction of the 
one-dimensional spectrum are described in \citet{Bacon01} and 
\citet{Aldering06}. 
Flux calibration was performed using a separate pipeline described in \citet{Mann15}.

\teff\ was calculated by comparing our optical spectra with the CFIST
suite\footnote{http://phoenix.ens-lyon.fr/Grids/BT-Settl/CIFIST2011/} of the BT-SETTL
version of the PHOENIX atmosphere models \citep{Allard13}, which gave a temperature
of 3503 $\pm$ 60\,K. 
More details of this procedure are given in \citet{Mann14} and
\citet{Gaidos14}. 
This method was used because it is known to accurately reproduce empirical 
\teff\ values from long-baseline optical interferometry \citet{Boyajian12}.

Metallcity was determined using the procedures from \citet{Mann13a}, in which the
authors provide empirical relations between atomic features and M dwarf
metallicity, calibrated using wide binaries. 
We adopted the weighted mean of the $H-$ and $K-$band calibrations, 
which yielded a metallicity of 0.09$\pm$0.09.

We combined the derived \teff\ and [Fe/H] values with the empirical 
\teff-[Fe/H]-$R_*$ relation from \citet{Mann15} to compute a radius. 
Accounting for measurement and calibration errors in [Fe/H] and \teff\ we calculated 
a radius 0.394$\pm0.038R_\odot$. 
We use these parameters instead of the derived photometric properties for this target.

@@

\bibliography{exopapers}
